\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-12 paper/draft.tex
Update techniques

\usepackage{soul}
\usepackage{xspace}
\usepackage{color}
\usepackage{booktabs}
\usepackage{graphicx}

@@

% ATTRIBUTION
% Interestingly, profiling functions running at each boundary cannot ``see through'' libraries in order to attribute load among a library and its dependencies correctly.
% For example, an agent at the outermost boundary \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency\eat{ is \ttt{A}-internal and how much} comes from \ttt{B}. % or \ttt{B}'s dependency, \ttt{C}.
%

@@

\heading{Context Linking}
To link the library with the newly transformed version of its context, \sys wraps the library---still an uninterpreted string of source code---with a closure.
The closure's body starts with a prologue of the form:
\begin{verbatim}
  pint = ctx.print
  error = ctx.error
  ...
\end{verbatim}
These statements shadow global variable names by redefining them as local ones.
The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
The prologue executes before everything else in the library.
% When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.

@@

The following subsections outline how module systems handle modules at runtime, by exemplifying the internals of Node.js.
It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.

In practice, the aforementioned dialysis stages can be implemented in two different ways.
The first is as a modified version of the runtime, where 
No-op analyses correspond to the default execution
  either 
It is introduced as a backward-compatible, drop-in replacement of the language's module system.
It can be imported as an application-specific module (\eg \ttt{ignis} package) or can be bundled with a custom language runtime (\eg \sys-powered Lua) replacing its system-wide module system.

We went with the latter approach, providing \sys as a library, to simplify its evaluation and its comparison with the vanilla runtime (both in terms of performance and correctness).
However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
  we expand on these at the end of this section~\sx{opportunities}.
% get second argument, no need to pass arguments around, tricky to 
% carefull hardcoding of paths, because \sys's code itself is split into modules
% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
% This is useful, for example, when...
% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;

(1) why node.js
(2) Create a table of compatibility and show individual aspects

\heading{Module System}
Node.js' module system is implemented entirely in JavaScript.
It exposes \ttt{require}, a global-looking function for importing modules.
\fixme{Figure} above demonstrates the use of \ttt{require}.

% \begin{lstlisting}[language=js,mathescape,upquote=true]
% // -------------- [./main.js] -------------
% // importing point
% let Point = require("./point.js");
% Point.create(1, 1).print(); // => [1, 1]
% 
% // -------------- [./point.js] ------------
% let Point = function Point (x, y) {
%     this.x = x; this.y = y;
% };
% Point.prototype.print = function print () {
%   console.log([this.x, this.y]);
% };
% module.exports = {
%     create:  function create (x, y) {
%         return new Point(x, y);
%     }
% };
% \end{lstlisting}

In the example above, the main module (\ttt{main.js}) imports the \ttt{point.js} module using the \ttt{require} statement (line 3)
Functionality from the exporting module (\ttt{point.js}) that is expected to become available to the importing module (\ttt{main.js}) is assigned to a special \ttt{module.exports} object (line 13);
  the rest is module-private functionality.
Files and modules are in one-to-one correspondence (each file is treated as a separate module).
Method \ttt{require} is synchronous (\ie blocking):
  it will block execution until the module specified is loaded.
% ---and can be used to load built-in modules such as \ttt{http} and \ttt{fs}.
The module system is implemented in the \ttt{module} built-in module~\sx{c}, which locates, wraps, compiles, and executes the specified file.

\sys hooks into \ttt{module} and alters the return value of the \ttt{require} call that imports \ttt{point.js} (line 3).

\subsection{Implementation of the Module System}
\label{c}

>>>>

\usepackage{soul}
\usepackage{xspace}
\usepackage{color}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{alltt}
\usepackage{amssymb}
\usepackage{amsmath}

@@

@@

\heading{Context Linking}
To link the library with the newly transformed version of its context, \sys wraps the library---still an uninterpreted string of source code---with a closure.
The closure's body starts with a prologue of the form:
\begin{verbatim}
  local pint = ctx.print
  local error = ctx.error
  ...
\end{verbatim}
These statements shadow global variable names by redefining them as local ones.
The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
The prologue executes before everything else in the library.
% When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.

@@

\section{Implementation of Dialysis for SSJ}
\label{impl}
